The design and implementation of standards-based Grid single sign-on using federated identity

### 2009-05-01 doc/sec/papers/GRID09/paper.tex
minor changes

%-------------------------------------------------------------------------
\section{Bridging federated identity and X.509 credential}
\label{sec:fedidtoX509}
Many widely used Grid middlewares are based on GSI which requires mutual X.509
authentication. Meanwhile, Web Service based Grid applications mostly require client
certificate authentication. To bridge the gap between federated identities and X.509 credentials, a short
lived credential service (SLCS) is implemented through which a user can get a short-lived X.509
certificate only by providing his username and password and authenticating through the SAML2SSO
profile.

@@

%-------------------------------------------------------------------------
\section{Performance Evaluation}
\label{sec:perfeval}
The following sections evaluate the performance of the HED versus Axis2/C, as 
well as the performance related to the SAML2SSO profile, short-lived credential
service, and delegation service.

\subsection{Performance comparison between HED and Axis2/C}
\label{sec:perhedandaxis}
Since the implementation of HED includes an alternative SOAP implementation
which is the base of the security related web services described in this paper, it is useful to
compare the performance of HED and other SOAP implementations. Although there are many SOAP
implementations such as AxisJava, gSOAP, XSOAP4, etc.., it is not the goal of this paper to do a
complete comparison between HED and all the other SOAP implementations, so we use Axis2/C (v1.5.0) to
demonstrate the performance HED.

For the service side, we implement two simple ``echoString'' services in HED and
Axis2/C. The ``echoString'' provides a simple SOAP portType which will output the same value
as it gets from input. For the client side, we developed a client by using the client API of ARC, to
invoke ``echoString'' services from Axis2/C and HED. Service invocation just sends a short
string to a service, and gets back the same string. One test involves a set of clients
which run simultaneously. Each client runs for a fixed period of time, and invokes the service as many
times as it can during the test period. Multiple clients are launched by creating multiple threads in
one test. Two values are measured: average response time and throughput. Average response
time is computed by counting the average value of the response time for each invocation.
Throughput is computed by counting number of invocations per second.

>>>>

%-------------------------------------------------------------------------
\section{Bridging federated identity and X.509 credential}
\label{sec:fedidtoX509}
The integration of SAML2SSO profile in Section~\ref{sec:intergrationSAML2SSO}
provides complete single sign-on in the Grid middleware level without requiring X.509
certificate on the client side.

However, many widely used Grid middlewares are based on GSI which requires mutual X.509
authentication. Meanwhile, Web Service based Grid applications mostly require client
certificate authentication. To bridge the gap between federated identities and X.509 credentials, a short
lived credential service (SLCS) is implemented through which a user can get a short-lived X.509
certificate only by providing his username and password and authenticating through the SAML2SSO
profile.

@@

%-------------------------------------------------------------------------
\section{Performance Evaluation}
\label{sec:perfeval}
The following sections evaluate the performance of the HED versus Axis2/C, as 
well as the performance related to the integration of SAML2SSO profile, 
short-lived credential service, and delegation service.

\subsection{Performance comparison between HED and Axis2/C}
\label{sec:perhedandaxis}
Since the implementation of HED includes an alternative SOAP implementation
which is the base of the security related web services described in this paper, it is useful to
compare the performance of HED and other SOAP implementations. Although there are many SOAP
implementations such as AxisJava, gSOAP, XSOAP4, etc.., it is not the goal of this paper to do a
complete comparison between HED and all the other SOAP implementations, so we use Axis2/C (v1.5.0) to
demonstrate the performance of HED.

For the service side, we implement two simple ``echoString'' services in HED and
Axis2/C. The ``echoString'' provides a simple SOAP portType which will output the same value
as it gets from input. For the client side, we develope a client by using the client API of ARC, to
invoke ``echoString'' services from Axis2/C and HED. Service invocation just sends a short
string to a service, and gets back the same string. One test involves a set of clients
which run simultaneously. Each client runs for a fixed period of time, and invokes the service as many
times as it can during the test period. Multiple clients are launched by creating multiple threads in
one test. Two values are measured: average response time and throughput. Average response
time is computed by counting the average value of the response time for each invocation.
Throughput is computed by counting number of invocations per second or per minute.
